Hierarchical model assessing the impacts of time to detection distribution assumptions on detection probability estimation

### 2016-09-08 Draft.tex
Add institution
Eliminate unnecessary packages and commands

\documentclass[useAMS,usenatbib,referee,12pt]{article}
\usepackage[margin=1.0in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{parskip}
\usepackage[round]{natbib}
\usepackage{color}
\usepackage[dvipsnames]{xcolor}
\usepackage{caption}
\usepackage{tabularx, booktabs}
\usepackage{float}
\usepackage{adjustbox}
\usepackage[toc,page]{appendix}
\usepackage{enumitem}
\usepackage{multirow}
\usepackage{setspace}
\usepackage{url}
\usepackage{xr}
\externaldocument[S-]{Supplement}
\doublespacing

@@

\newcommand{\adam}[1]{{\color{blue} ADAM: #1}}
\newcommand{\jarad}[1]{{\color{Orange} JARAD: #1}}
\newenvironment{indpar}[1]%
     {\begin{list}{}%
             {\setlength{\leftmargin}{#1}}%
             \item[]%
     }
     {\end{list}}

@@

@@

\author{Adam Martin-Schwarze, Jarad Niemi, and Philip Dixon}

@@

The results from this simulation are qualitatively similar to that Ovenbird analysis (Figure \ref{ovenposteriors}) and thus we only briefly review the results here and provide the corresponding figures and tables in the Supplementary Material. 
Patterns in posterior estimates of site-specific detection probabilities, $\pdet_s$, with respect to mixture and family TTDD forms were the same as in the previous simulation studies -- the inclusion of explanatory variables did not make models more robust to violations of mixture- and constant-detection assumptions (Figures \ref{S-pdet_cater_correct} and \ref{S-pdet_cater_family}).  
Posteriors for abundance fixed and random effects were the same regardless of what TTDD was assumed (Section \ref{S-s:sim3}).  
Posteriors for the mixing parameter $\gamma$ and detection fixed and random effects were the same across gamma, lognormal, and Weibull mixture models but were narrower and location-shifted for the exponential mixture model.  
%It should be remembered that detection covariate effect estimates are conditional on the estimated mixing parameter $\gamma$.

>>>>

\documentclass[12pt]{article}
\usepackage[margin=1.0in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{parskip}
\usepackage{natbib}
% \usepackage{color}
% \usepackage[dvipsnames]{xcolor}
\usepackage{caption}
%\usepackage{tabularx, booktabs}
%\usepackage{float}
\usepackage{adjustbox}
\usepackage[toc,page]{appendix}
\usepackage{enumitem}
\usepackage{multirow}
\usepackage{setspace}
\usepackage{url}
\usepackage{xr}

\externaldocument[S-]{Supplement}

\doublespacing

@@

% \newcommand{\adam}[1]{{\color{blue} ADAM: #1}}
% \newcommand{\jarad}[1]{{\color{Orange} JARAD: #1}}

\newenvironment{indpar}[1]%
     {\begin{list}{}%
             {\setlength{\leftmargin}{#1}}%
             \item[]%
     }
     {\end{list}}

@@

\providecommand{\blind}{0}

@@

\if0\blind
\author{Adam Martin-Schwarze, Jarad Niemi, and Philip Dixon\\
Department of Statistics, Iowa State University, Ames, Iowa}
\fi

@@

The results from this simulation are qualitatively similar to that Ovenbird analysis (Figure \ref{ovenposteriors}) and thus we only briefly review the results here and provide the corresponding figures and tables in the Supplementary Material. 
Patterns in posterior estimates of site-specific detection probabilities, $\pdet_s$, with respect to mixture and family TTDD forms were the same as in the previous simulation studies -- the inclusion of explanatory variables did not make models more robust to violations of mixture- and constant-detection assumptions (Figures \ref{S-pdet_cater_correct} and \ref{S-pdet_cater_family}).  
Posteriors for abundance fixed and random effects were the same regardless of what TTDD was assumed, see Section \ref{S-s:sim3} and figures therein.  
Posteriors for the mixing parameter $\gamma$ and detection fixed and random effects were the same across gamma, lognormal, and Weibull mixture models but were narrower and location-shifted for the exponential mixture model.  
%It should be remembered that detection covariate effect estimates are conditional on the estimated mixing parameter $\gamma$.
